Trends of SDR in Thessaloniki

### 2023-11-06 Build_159/MDPI_submission_B159.Rmd
Commit 2023-11-06 09:11

---
title:     "Trends of SDR in Thessaloniki"
author:
  - name:  Athanasios Natsis
    affil: 1,* # \ddagger
    orcid: 0000-0002-5199-4119
  - name: Alkiviadis Bais
    affil: 2, #\dagger, # \ddagger
affiliation:
  - num: 1
    address: |
      Aristotle University of Thessaloniki -
      Laboratory of Atmospheric Physics,
      Campus Box 149, 54124 Thessaloniki, Greece
    email: natsisphysicist@gmail.com (A.N.); abais@auth.gr (A.B.)
  - num: 2
    address: |
      Your department
      Street, City, Country
#     email: abais@auth.gr
# author citation list in chicago format
authorcitation: |
  Natsis, A.; Bais, A.
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  natsisphysicist@gmail.com;
#   Tel.: +XX-000-00-0000.

@@

supplementary: |
 The following supporting information can be downloaded at:
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.

@@

The shortwave downward solar irradiance (SDR) at Earth's surface plays a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycles [@Wild2009].
It can also affect solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term 'brightening' is generally used to describe periods of positive SDR trend, and 'dimming' for negative trend.
There are many cases in the long term records of irradiance, showing a systematic change in the magnitude of the trend, occurring roughly in the last decades of the 20th century.
<!-- Trends china -->
On multiple stations in China, a dimming period was reported until about 2000, followed by a brightening period [@Yang2021].
<!-- Trends Europe Brazil -->
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe [@Wild2021] and Brazil [@Yamasoe2021].
<!-- Trends Global -->
On global scale, an artificial Intelligence aided spatial analysis on continental level with data from multiple stations reach similar conclusions for these regions and for the global trend [@Yuan2021].

@@

For completeness, we will provide below a brief overview of the clear sky identification algorithm (CSid), along with the site specific thresholds.
To calculate the reference clear sky $\text{SDR}_\text{CSref}$ we used the $\text{SDR}_\text{Haurwitz}$ derived by the radiation model of @Haurwitz1945, adjusted for our site with a factor $a$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process, as described by @Long2000 and @Reno2016.
The target of the optimization was the minimization of a function $f(a)$ (Eq.\ \ref{eq:minf}) and was accomplished with the algorithmic function "optimise", which is an implementation based on the work of @Brent1973, from the library "stats" of the R programming language [@RCT2023].
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (namely, Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), while the procedure, manages to characterize the majority of the data.
Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.
<!-- cost fuction -->
\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation}
where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is any of the tested clear sky radiation models.
<!-- adjusted Haurwitz -->
\begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = `r signif(alpha,3)` \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation}
where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{W}\,\text{m}^{-2}$ and $\theta$ is the solar zenith angle (SZA).

@@

--------------------

@@

# Discussion

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The findings and
their implications should be discussed in the broadest context possible. Future
research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

>>>>

---
title:     "Trends of SDR in Thessaloniki"
author:
  - name:  Athanasios Natsis
    affil: 1,* # \ddagger
    orcid: 0000-0002-5199-4119
  - name: Alkiviadis Bais
    affil: 1 #, \dagger, # \ddagger
affiliation:
  - num: 1
    address: |
      Aristotle University of Thessaloniki -
      Laboratory of Atmospheric Physics,
      Campus Box 149, 54124 Thessaloniki, Greece
    email: natsisphysicist@gmail.com (A.N.); abais@auth.gr (A.B.)
  # - num: 2
  #   address: |
  #     Your department
  #     Street, City, Country
#     email: abais@auth.gr
# author citation list in chicago format
authorcitation: |
  Natsis, A.; Bais, A.
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  natsisphysicist@gmail.com;
#   Tel.: +XX-000-00-0000.

@@

# supplementary: |
#  The following supporting information can be downloaded at:
#  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.

@@

The shortwave downward solar irradiance (SDR) at Earth's surface plays a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycles [@Wild2009].
It can also affect solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term 'brightening' is generally used to describe periods of positive SDR trend, and 'dimming' for negative trend [@Wild2009].
There are many cases in the long term records of irradiance, showing a systematic change in the magnitude of the trend, occurring roughly in the last decades of the 20th century.
<!-- Trends china -->
On multiple stations in China, a dimming period was reported until about 2000, followed by a brightening period [@Yang2021].
<!-- Trends Europe Brazil -->
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe [@Wild2021] and Brazil [@Yamasoe2021].
<!-- Trends Global -->
On global scale, an artificial Intelligence aided spatial analysis on continental level with data from multiple stations reach similar conclusions for these regions and for the global trend [@Yuan2021].

@@

For completeness, we will provide below a brief overview of the clear sky identification algorithm (CSid), along with the site specific thresholds.
To calculate the reference clear sky $\text{SDR}_\text{CSref}$ we used the $\text{SDR}_\text{Haurwitz}$ derived by the radiation model of @Haurwitz1945, adjusted for our site with a factor $a$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process, as described by @Long2000 and @Reno2016.
The target of the optimization was the minimization of a function $f(a)$ (Eq.\ \ref{eq:minf}) and was accomplished with the algorithmic function "optimise", which is an implementation based on the work of @Brent1973, from the library "stats" of the R programming language [@RCT2023].
<!-- cost function -->
\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation}
where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is any of the tested clear sky radiation models.
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (namely, Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), while the procedure, manages to characterize the majority of the data.
Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.
<!-- adjusted Haurwitz -->
\begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = `r signif(alpha,3)` \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation}
where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{W}\,\text{m}^{-2}$ and $\theta$ is the solar zenith angle (SZA).

@@

<!-- ------------------------------------------------------------ -->

@@

<!-- # Discussion -->

<!-- Authors should discuss the results and how they can be interpreted in -->
<!-- perspective of previous studies and of the working hypotheses. The findings and -->
<!-- their implications should be discussed in the broadest context possible. Future -->
<!-- research directions may also be highlighted. -->

<!-- # Conclusion -->

<!-- This section is not mandatory, but can be added to the manuscript if the -->
<!-- discussion is unusually long or complex. -->
